A comparative risk assesment of U.S. regional active transport using the ITHIM model

### 2016-10-05 manuscript/manuscript.tex
Working on edits to Methods section of manuscript.

\newcommand{\col}[2][red]{\textcolor{#1}{#2}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\package}{\emph{ITHIM}}
\newcommand{\ithim}{\emph{ITHIM}}
\newcommand{\R}{\emph{R}}
\newcommand{\sgy}[1]{{\itshape\col{#1}}}
\newcommand{\XX}{\sgy{XX}}
\newcommand{\webpage}{\url{http://www.ithim.ghi.wisc.edu}}
\newcommand{\af}{\rho}
\newcommand{\mets}{MET-hrs./week}
\newcommand{\pEm}[1]{$\mathrm{PM}_{#1}$}
\newcommand{\vmt}{$\mathrm{VMT}$}

@@

\textit{
    The ITHIM model uses the comparative risk
    assesment framework to estimate the population attributable
    fraction, $\af$.  In our case $\af$ represents the proportional
    change in mortality and morbidity if the physical activity levels
    were adjusted to represent an alternate scenario.
}

@@

\textit{ Here $R(x)$ represents the risk when the individual has
  exposure $x$, in our case physical activity (\mets).  $P(x)$ and
  $Q(x)$ denote the population density of individuals with exposure
  $x$, in the baseline and alternate scenarios, respectively.  The
  exposure variable, $x$, is modeled as the sum of travel-related
  exposure and non-travel-related exposure.}

@@

\section{Seven State Analysis}
\begin{itemize}
\item We used the National Household Transportation Survey \cite{NHTS} to
  estimate the mean walk and cycle times for individuals that live in
  metropolitan areas ($\textrm{DAYV2PUB.MSA} \in (1,2,\ldots,5)$ which
  corresponds to individuals whose homes are in an MSA or cMSA)
  \bi\item Data quality issues along with assumptions about travel speed
created mirky data.  The median values of trip time were used to avoid
undue influence by outliers.\ei
\item We then divided these into the 10 regions of the U.S. defined by
  the Department of Health and Human Services (HH1-10)
\item Using only the active transport component of the ITHIM model we
  ran comparative analyses for each of the ten regions, using the
  national averages as the baseline.
\item We used data from the American Time Use Survey \cite{ATUS} to
  estimate the relative means for each of the age-sex strata.  We then
  treat the mean of the referent group as a variable and compute
  results over a grid of values for this variable.  See Figure
  \ref{dalyFigure}.
\item Values for DALYs were found using the CDC Wonder database \cite{CDCWonder}
\end{itemize}

%% \begin{figure}[t]
%%     \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig2}}
%%     \caption{Change in total national DALYs for each regional
%%       transportation estimates.}\label{dalyFigure}
%% \end{figure}

>>>>

\newcommand{\col}[2][red]{\textcolor{#1}{#2}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\package}{\emph{ITHIM}}
\newcommand{\ithim}{\emph{ITHIM}}
\newcommand{\R}{\emph{R}}
\newcommand{\sgy}[1]{{\itshape\col{#1}}}
\newcommand{\XX}{\sgy{XX}}
\newcommand{\webpage}{\url{http://www.ithim.ghi.wisc.edu}}
\newcommand{\af}{\textrm{PAF}}
\newcommand{\mets}{MET-hrs./week}
\newcommand{\pEm}[1]{$\mathrm{PM}_{#1}$}
\newcommand{\vmt}{$\mathrm{VMT}$}

@@

The ITHIM model uses the comparative risk assesment framework to
estimate the population attributable fraction, $\af$.  In our case the
$\af$ represents the proportional change in national disease burden if
age and sex-specific active transport time means were changed.

@@

Here $R(x)$ represents the risk when the individual has exposure $x$,
physical activity (\mets).  $P(x)$ and $Q(x)$ denote the population
density of individuals with exposure $x$, in the baseline and
alternate scenarios, respectively.  The exposure variable, $x$, is
modeled as the sum of travel-related exposure and non-travel-related
exposure, which are modeled as two independent random variables.  The
age-sex specific mean ratios for non-travel-related exposure are
estimated from the ATUS \cite{ATUS} and the referent group mean is
treated as a variable.  We see in Figure \ref{dalyFigure} that varying
it does not greatly affect the estimate for disease burden.

@@

\section{New York and California}

\begin{itemize}
\item We used the National Household Transportation Survey \cite{NHTS} to
  estimate the mean walk and cycle times for individuals that live in
  metropolitan areas ($\textrm{DAYV2PUB.MSA} \in (1,2,\ldots,5)$ which
  corresponds to individuals whose homes are in an MSA or cMSA)
  \bi\item Data quality issues along with assumptions about travel speed
created mirky data.  The median values of trip time were used to avoid
undue influence by outliers.\ei
\item We then divided these into the 10 regions of the U.S. defined by
  the Department of Health and Human Services (HH1-10)
\item Using only the active transport component of the ITHIM model we
  ran comparative analyses for each of the ten regions, using the
  national averages as the baseline.
\item We used data from the American Time Use Survey \cite{ATUS} to
  estimate the relative means for each of the age-sex strata.  We then
  treat the mean of the referent group as a variable and compute
  results over a grid of values for this variable.  See Figure
  \ref{dalyFigure}.
\item Values for DALYs were found using the CDC Wonder database \cite{CDCWonder}
\end{itemize}

\begin{figure}[t]
    \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig2}}
    \caption{Change in total national DALYs for each regional
      transportation estimates.}\label{dalyFigure}
\end{figure}
